---
title: Selection Demo of US Navy Billets
date: "Date: `r Sys.Date()`"
output:
  html_document:
    keep_md: yes
    toc: yes
  md_document:
    variant: markdown_github
---

This report demonstrates one approach to optimally match officers and ER billets.  The project is under the initial direction of [Richard C. Childers](mailto:richard.childers@navy.mil), CDR NPC, PERS-4415, with advisement from [Alvin Roth](http://web.stanford.edu/~alroth/).

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F} 
# cat("Working directory: ", getwd())
  library(knitr)
  opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# cat("Working directory: ", getwd())
opts_chunk$set(
  results    = 'show', 
  comment    = NA, 
  tidy       = FALSE,
  fig.width  = 4, 
  fig.height = 4, 
  fig.path   = 'figure-png/'
)
# dpi = 400,
# out.width = "650px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.

echoChunks <- FALSE
options(width=100) #So the output is 25% wider than the default.
read_chunk("./analysis/select-1/select-1.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```

<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echoChunks, message=FALSE}
```

<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echoChunks, message=FALSE}
```

<!-- Load any global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
#Put presentation-specific code in here.  It doesn't call a chunk in the codebehind file.
```

<!-- Load the datasets.   -->
```{r load-data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echoChunks, results='show', message=FALSE}
```

Summary
===========================================

### Notes 
1. The current demonstration covers `r nrow(ds_officer_roster)` officers, `r nrow(ds_hospital_roster)` unique hospitals, and `r sum(ds_hospital_roster$billet_count_max)` total possible billets.
1. Although there can be multiple billets per hospital, an officer ranks the global hospital, instead of a specific billet.  Similarly, the hospital ranks an officer, instead of a billet ranking an officer.  The billet capacity of a hospital is accommodated during the matching process.

### Sources
1. This demonstration was developed primarily by [Will Beasley](http://ouhsc.edu/bbmc/team/), Assistant Professor of Research, University of Oklahoma College of Medicine, [Department of Pediatrics](http://www.oumedicine.com/pediatrics).  The code developed for the billet marketplace project is open source and [available online](https://github.com/OuhscBbmc/usnavy-billets).  
1. The project members are appreciative of the open source [`matchingMarkets`](https://cran.r-project.org/package=matchingMarkets) R package, (independently developed by [Thilo Klein](https://github.com/thiloklein) since [2013](https://github.com/thiloklein/matchingMarkets/commits/master)) that implements the Gale-Shapley (1962) Deferred Acceptance Algorithm. For further discussion, see [Roth, 2007](https://dash.harvard.edu/bitstream/handle/1/2579651/Roth_Deferred%20Acceptance.pdf) and the [2012 Nobel Prize material](http://www.nobelprize.org/nobel_prizes/economic-sciences/laureates/2012/press.html).
1. The most recent version of this demonstration report is available at https://github.com/OuhscBbmc/usnavy-billets/blob/master/analysis/select-1/select-1.md.

### Unanswered Questions

1. How should the process be adjusted to accommodate issues like (a) recent tours overseas, (b) seniority, and (c) cliques?

### Answered Questions

 1. --

# Raw Rankings

These two tables represent the raw/initial rankings provided from each hospital (in the first table) and from each officer (in the second table).  No adjustments have been made yet to the rankings.

In the first table (i.e., "Input from Each *Hospital*"), each row represents an officer being ranked; each column represents a hospital providing their preferences.  In constrast, in the second table (i.e., "Input Provided from Each *Officer*"), each row represents a hospital being ranked; each column represents an officer providing their preferences.

To walk through an example from the hospital's perspective, look at the fifth row in the first table.  The values represent how the `r nrow(ds_hospital_roster)` hospitals ranked officer ```r ds_hospital$officer_id[5]```.  The first four hospitals (i.e., ```r paste(colnames(ds_hospital)[2:5], collapse=", ")```) ranked officer ```r ds_hospital$officer_id[5]``` as `r as.data.frame(ds_hospital[5, 2:4])`, and `r as.data.frame(ds_hospital[5, 5])`.

To walk through an example from the officer's perspective, look at the second row in the second table.  The values represent how the `r nrow(ds_officer_roster)` officers ranked hospital ```r ds_officer$hospital_id[2]```.  The first four officers (i.e., ```r paste(colnames(ds_officer)[2:5], collapse=", ")```) ranked officer ```r ds_officer$hospital_id[2]``` as `r as.data.frame(ds_officer[2, 2:4])`, and `r as.data.frame(ds_officer[2, 5])`.

```{r rankings-raw, echo=echoChunks, message=TRUE, results='asis'}
```

Results
===========================================

Matches
-------------------------------------------

The skinny table below shows the pairs of hospital--officer matches.  Notice that not all entities were matched.  This is because there were `r sum(ds_hospital_roster$billet_count_max)` total billets (across `r nrow(ds_hospital_roster)` unique hospitals), but `r nrow(ds_officer_roster)` officers.
```{r match, echo=echoChunks, message=TRUE}
```

Display
-------------------------------------------

The final table shows the indices of only the successful matches, along with the following information:

* the hopsital ID and name (`hospital id` and `hospital name`), 
* the maximum number of billets for a hospital (`billet count max`),
* the officer ID and name  (`officer id` and `officer name last`), 
* the preference expressed from the hospital for the officer (`preference from hospital`)
* the preference expressed from the officer for the hospital (`preference from officer`)

In this dmeonstration, notice that not all hospitals filled every billet.

```{r display, echo=echoChunks, message=TRUE, fig.width=7}
```


Session Information
===========================================

For the sake of documentation and reproducibility, the current report was rendered on a system using the following software.

```{r session-info, echo=FALSE}
cat("Report rendered by", Sys.info()["user"], "at", strftime(Sys.time(), "%Y-%m-%d, %H:%M %z"))
sessionInfo()
```
