---
title: US Navy Billets  --Selection Demo
date: "Date: `r Sys.Date()`"
output:
  html_document:
    keep_md: yes
    toc: yes
---

This report demonstrates one approach to optimally match officers and ER billets.  The project is under the initial direction of [Richard C. Childers](mailto:richard.childers@navy.mil), CDR NPC, PERS-4415, with advisement from [Alvin Roth](http://web.stanford.edu/~alroth/).

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F} 
# cat("Working directory: ", getwd())
  library(knitr)
  opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# cat("Working directory: ", getwd())
opts_chunk$set(
  results    = 'show', 
  comment    = NA, 
  tidy       = FALSE,
  fig.width  = 4, 
  fig.height = 4, 
  fig.path   = 'figure-png/'
)
# dpi = 400,
# out.width = "650px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.

echoChunks <- FALSE
options(width=100) #So the output is 25% wider than the default.
read_chunk("./analysis/select-1/select-1.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```

<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echoChunks, message=FALSE}
```

<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echoChunks, message=FALSE}
```

<!-- Load any global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
#Put presentation-specific code in here.  It doesn't call a chunk in the codebehind file.
```

<!-- Load the datasets.   -->
```{r load-data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echoChunks, results='show', message=FALSE}
```

# Summary

### Notes 
1. The current report covers `r nrow(ds_officer_roster)` officers, `r nrow(ds_hospital_roster)` unique hospitals, and `r sum(ds_hospital_roster$billet_count_max)` total possible billets.
1. Although there can be multiple billets per hospital, an officer ranks the global hospital, instead of a specific billet.  Similarly, the hospital ranks an officer, instead of a billet ranking an officer.  The billet capacity of a hospital is accommodated during the matching process.
1. This demonstration was developed by [Will Beasley](http://ouhsc.edu/bbmc/team/), Assistant Professor of Research, University of Oklahoma College of Medicine, [Department of Pediatrics](http://www.oumedicine.com/pediatrics).

### Unanswered Questions

### Answered Questions


# Raw Rankings
These two table represent the raw/initial rankings provided from each hospital (in the first table) and from each officer (in the second table).  No adjustments have been made yet to the rankings.

In the first table (i.e., "Input from Each *Hospital*"), each row represents an officer being ranked; each column represents a hospital providing their preferences.  In constrast, in the second table (i.e., "Input Provided from Each *Officer*"), each row represents a hospital being ranked; each column represents an officer providing their preferences.

To walk through an example, look at the fifth row in the first table.  The values represent how the `r nrow(ds_hospital_roster)` hospitals ranked officer `r ds_hospital$officer_id[5]`.  The first four hospitals (i.e., `r paste(colnames(ds_hospital)[2:5], collapse=", ")`) ranked officer `r ds_hospital$officer_id[5]` as `r as.data.frame(ds_hospital[5, 2:4])`, and `r as.data.frame(ds_hospital[5, 5])`.

```{r rankings-raw, echo=echoChunks, message=TRUE, results='asis'}
```

# Select

```{r select, echo=echoChunks, message=TRUE}
```

# Join

```{r join, echo=echoChunks, message=TRUE, fig.width=7}
```


# Session Information
For the sake of documentation and reproducibility, the current report was rendered on a system using the following software.

```{r session-info, echo=FALSE}
cat("Report rendered by", Sys.info()["user"], "at", strftime(Sys.time(), "%Y-%m-%d, %H:%M %z"))
sessionInfo()
```
